Phenotypic evolution is more constrained in simpler food webs

### 2019-05-13 manuscript.Rmd
added caveats paragraph in Discussion.

>>>>

<!-- Caveats -->
Our study has some limitations to consider when relating our findings to the effects of consumer extinctions on evolutionary constraints more generally. First, we removed other sources of mortality prior to our analyses. While this was necessary to avoid confounding estimates of selection with effects on phenotypic expression, we may be overestimating the effects of selection due to parasitoids. Second, our metrics of evolutionary constraints do not account for variation in the magnitude of selection pressures. While quantitative metrics are possible and more ideal [@Hansen2008], we felt they were not appropriate to apply here as our experimental removal of larval parasitoids results in a transient dynamic in the strength (but not direction) of selection. Such transient dynamics may be common in short-term experimental studies of natural selection, but they can be detected by using natural history information and dissecting the sources of selection (e.g. quantifying selection surfaces and treatment effects on mean fitness) as we did here.
